Secontrails plots

### 2022-02-01 R/Secontrails plots.Rmd
scdtrailadj WIP

# Data
```{r}
# save(secondtrails, file = "../data/secondtrails.Rdata")
data("HarvestablePolygons")
data(DTMParacou)
data(CreekDistances)
data("MainTrails")
```

# Def UP
```{r}
HarvestableAreaOutputs27 <- harvestableareadefinition(
  topography = DTMParacou,
  creekdistances = CreekDistances,
  advancedloggingparameters = loggingparameters(MaxAreaSlope = 27)
)
HarvesPolygons22 <-  HarvestableAreaOutputs$HarvestablePolygons
HarvesPolygons27 <-  HarvestableAreaOutputs27$HarvestablePolygons

@@

>>>>

# Data
```{r}
# save(secondtrails, file = "../data/secondtrails.Rdata")
data("HarvestablePolygons")
data(DTMParacou)
data(CreekDistances)
data(PlotMask)
data("MainTrails")
```

# Def UP
```{r}
HarvestableAreaOutputs <- harvestableareadefinition(
  topography = DTMParacou,
  creekdistances = CreekDistances,
  plotmask = PlotMask,
  scenario = "RIL2"
)
HarvesPolygons22 <-  HarvestableAreaOutputs$HarvestablePolygons
HarvesPolygons27 <-  HarvestableAreaOutputs27$HarvestablePolygons

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +
